---
title: "Manuscript 3 - Stroke Caregiver Burden Bibliometric"
subtitle: "Research on Stroke Caregiver Burden, A bibliometric Analysis"
author: "Mohd Azmi B Suliman"
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format: 
  html:
    code-link: true
    code-fold: true
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: paged
    default-image-extension: svg
    embed-resources: true
    theme: sandstone
    fontsize: 1em
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    license: "CC BY"
toc: true
number-sections: true
execute: 
  warning: false
  cache: false
monofont: 'Fira Code'
---

# Front Matter

Title: Research on Stroke Caregiver Burden, A bibliometric Analysis

Authors:

## Abstract

**Introduction**: Stroke is a serious and growin ghelath problem, and since most people with stroke live at home, caring responsibilities generally fall on family mmembers. Caregivers are often inadequately supported by formal health services and have poorer psychological and physical health. Our study aimed to compare the contribution of publications from different countries, instituiton and authors and present a bibliometric analysis to determine the hotspots and trend in research concerning the health and interventions for family stroke caregivers


**Methods**: Studies published during 1996-2021 were extracted from the Web of Science. Each abstract of publications was evaluated to obtain the basic information. 


Results:

Conclusion:

Keywords

# Introduction

# Methodology



# Results

```{r}
#| label: setup

pacman::p_load(tidyverse, bibliometrix, janitor, stringi, gtsummary, igraph, 
               gtsummary, kableExtra)

bibds_wos <- convert2df(file = "22-11-30 WOS_t100cgburden.bib", dbsource = "wos",
                        format = "bibtex")

```

```{r}
#| label: summary_setup

bibres <- biblioAnalysis(bibds_wos)

summary(bibres, k = 10)
```




# Discussion

# Conclusion


