---
title: "Manuscript 3 - Stroke Caregiver Burden Bibliometric"
subtitle: "Research on Stroke Caregiver Burden, A bibliometric Analysis"
author: "Mohd Azmi B Suliman"
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format: 
  html:
    code-link: true
    code-fold: true
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: paged
    default-image-extension: svg
    embed-resources: true
    theme: sandstone
    fontsize: 1em
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    license: "CC BY"
toc: true
number-sections: true
execute: 
  warning: false
  cache: true
monofont: 'Fira Code'
---

# Front Matter

Title: Research on Stroke Caregiver, A bibliometric Analysis

Authors:

## Abstract

**Introduction**: Stroke is a serious and growing health problem, and since most people with stroke live at home, caring responsibilities generally fall on family members. Caregivers are often inadequately supported by formal health services and have poorer psychological and physical health. Our study aimed to compare the contribution of publications from different countries, institution and authors and present a bibliometric analysis to determine the hotspots and trend in research concerning the health and interventions for family stroke caregivers

**Methods**: Studies published during 2003-2022 were extracted from the Web of Science (WOS). Each abstract of publications was evaluated to obtain the basic information. A bibliometric analysis was used to evaluate the number or cooperation networks of publications, countries, institution, journal, citations, authors, references and keywords. The resulting articles were analysed descriptively and the publication keywords were visualized using `bibliometrix` package in R.

Results: There were 152 publications were identified, with 104 of them were original articles. *Annually, approximately 10-15 articles were published. The USA has the highest number of publication (14.0%), followed by China and Turkey (both 10.0% respectively). The University Florida was the most productive institution while the Topics in Stroke Rehabilitation journal was the most productive journal. There were two authors that share the most productive authors, which were Grabowska-Fudala B and Jaracz K, both from Poland. A co-occurrence analysis of the keywords reveals a mainstream research focus on stroke survivors, family caregivers, quality of life, determinant, care and impact. The keyword "family caregivers", "nursing", and "quality of life" reflect the latest hotspots, appearing in approximately 2015-2021.*

Conclusion: Our study details the performance statistics, main topics and trend research on the health of and interventions for stroke caregivers from *1996-2021* and provides a comprehensive analysis.

Keywords: Bibliometric analysis; stroke caregivers burden; research trends

# Introduction

The majority of stroke survivors living at home were cared for by their spouses and children. Due to the ageing of the world population, the numbers of stroke survivors is expected to increase from by *xxx* by *2030*, however support services for caregivers are not expected to increase at the same rate.

::: callout-note
1 para (3-4 sentences) on stroke & stroke epidemiology
:::

The health of caregivers can be overlooked and they have been referred to as 'silent patients' or 'secondary patients'. The negative outcomes associated with caregiving include depression and anxiety, and caregivers exhibit high rates of mood disorders. The heavy burden and psychological distress caused by caring for relative with dementia may also contribute to severe physical and psychiatric problems and higher mortality risk. Recognizing this need, interventions have been developed to address the negative effect of caregiving, including education, respite, psychotherapeutic, family support, and multicomponent approaches. In recent decades, the research on this topic has covered a wide spectrum. However, a detailed analysis if the existing research publication landscape has not been undertaken to elucidate the body of published evidence. Such an analysis would be helpful for delineating the global trends in the research fields related to the health of and interventions for stroke caregivers.

::: callout-note
1-2 para (6-8 sentences) on stroke caregiver

-   epidemiology
-   need for intervention
:::

The aims of this study were to examine the publication patterns of research on stroke caregiver burden at a global level. we attempted to provide comprehensive insights into the current state of global research, including annual output characteristic, international collaborations, and keywords trends. The results should provide a better understanding of the global trends in the research on the stroke caregiver burden and indicate directions for further research.

::: callout-note
1 para for objectives and study justification
:::

# Methodology

The data were downloaded from public databases and as secondary data, did not require any interactions with human subjects. There were no ethical issues associated with the data, and approval from institutional review boards was not required.

The data were obtained from Web of Science on 1st December, 2022, with publications published in the past 20 years, between 2003 and 2022 were retrieved. The keyword used in the search were as follow: (TI=(stroke) AND TI=(caregiver)). *Two independent researchers* conducted the research simultaneously to ensure that the search was accurate and that all relevant manuscripts were identified and included. The search result form the Web of Science database were subsequently filtered to include the top 250 most cited, and limited to article type only. A bibtex data download from the WOS included the author names, contact address, title, publication year, abstract, author keyword, journal information and cited references.

Bibliometrics is defined as the application of statistics and mathematics for the analysis of written publications such as books and journal articles. Bibliometric techniques can be used to perform statistical and quantitative analysis of publications and offer a convenient way to visibly measure researchers efforts in the investigation of a specific field. Such analyses can characterize the development in certain field and have contributed substantially to informing policy making, clinical guidelines and research trends. Impact factors were taken from those published by the WOS in 2018. Cooperation among countries or institution was based on the first authors. Collaboration type was determined by the addresses of the authors, where the term 'single-country article' was assigned if the researchers' addresses were in the same country. The term 'internationally collaborative article' was used to designate those articles that were co-authored by researchers from multiple countries.

The data were analysed both quantitatively and qualitatively. We describe the research status of this field based on statistics regarding the number of articles and their distribution across countries and in time and space, subjects, journal, and high-yield institutions and authors. Moreover, the corpus was analysed to generate different scientific landscapes and networks. We analysed the cooperation situation in this field among countries and institutions via cooperation analysis; the intrinsic links among authors via bibliographic coupling; and the reference network and frequently cited literature via co-citation analysis. in the hotspot analysis, we captured high-frequency keywords for the clustering and co-occurrence analyses. The bibliometric analysis in this study was performed and visualized using `bibliometric` package in R and RStudio.

# Results

```{r}
#| label: setup
#| include: false

pacman::p_load(tidyverse, bibliometrix, janitor, stringi, gtsummary, igraph, 
               gtsummary, kableExtra, metagear)

bibds_wos <- convert2df(file = "22-11-30 WOS_TIstcgburden.ciw", dbsource = "wos",
                        format = "endnote")
bibres <- biblioAnalysis(bibds_wos)
# bibres_plot <- plot(bibres, k = 10)
# error for plot

bibres_countrylist <- bibres$Countries

bibres_countrytable <- tibble(Rank = seq_along(bibres_countrylist),
                              Country = rownames(bibres_countrylist),
                              Np = as.integer(bibres_countrylist)) %>% 
  mutate(Country = fct_reorder(Country, Rank))

bibres_aulist <- bibres$Authors

bibres_autable <- tibble(Rank = seq_along(bibres_aulist),
                         Author = rownames(bibres_aulist),
                         Np = as.integer(bibres_aulist))

bibres_autablepercent <- bibres_autable %>% 
  count(Np) %>% 
  mutate(percent = n / sum(n) * 100,
         percent = round(percent,1))

```

## General Information


```{r}
#| label: bibres_summary
#| include: false

bibres_summary <- summary(bibres, k = 10)
```


In total, 152 publications on the stroke caregiver burden published between `r min(bibres$Years, na.rm = T)` and `r max(bibres$Years, na.rm = T)` were identified through our search strategy using the WOS. Only `r bibres$Articles` original articles were identified and analysed. The papers were published by `r nrow(bibres$Authors)` authors in `r nrow(bibres$Sources)` sources and used `r nrow(bibres$DE)` keywords (after de-duplication). The total number of citations was `r sum(bibres$TotalCitation)`. The number of articles fluctuated, but generally growing steadily since 2006.

```{r}
#| label: fig-database_flow
#| fig-cap: "Flow diagram for the inclusion of publication on the stroke caregiver burden"
#| 

prismaplot <- plot_PRISMA(
  c("START_PHASE: Studies identified through databse searching (n=152)",
    "Publication Type: Articles only (n=104)",
    "EXCLUDE_PHASE: Other Type (n = 48)",
    "Included in the analysis (n=104)"),
  design = "classic", colWidth = 30, excludeDistance = 1
  )
```

```{r}
#| label: fig-annualscientprod
#| fig-cap: "Number of Publications by Year"

# bibres_plot$AnnualScientProd
# error plot - refer setup chunk

tibble(Article = rownames(bibds_wos),
       Year = bibds_wos$PY) %>% 
  group_by(Year) %>% 
  summarise(n = n()) %>% 
  add_row(Year = 1996:2022, n = 0) %>% 
  distinct(Year, .keep_all = T) %>% 
  ggplot(aes(x = Year, y = n)) +
  geom_area(alpha = .3) +
  geom_point() +
  geom_line() +
  scale_y_continuous(breaks = seq(0,16,2)) +
  scale_x_continuous(breaks = seq(1996,2022,2)) +
  coord_cartesian(ylim = c(0,16)) +
  labs(x = "Year", y = "Number of Publication") +
  theme_bw()
```


## Country

The 104 articles were published in `r nrow(bibres_countrylist)` countries, and the top 10 countries were shown in @fig-mostprodcountries. The collaboration network between the countries was shown in @fig-countries_collaboration.


```{r}
#| label: fig-mostprodcountries
#| fig-cap: "Number of Publication by top 10 countries" 

# bibres_plot$MostProdCountries
# error plot - refer setup chunk

bibres_countrytable %>%
  filter(Rank <= 10) %>%
  ggplot(aes(x = Np, y = Country)) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0,15,2)) +
  labs(x = "Number of Publications") +
  theme_bw()
  
```

```{r}
#| label: fig-countries_collaboration
#| fig-cap: "Countries Collaboration Map" 

bib_concolab <- metaTagExtraction(bibds_wos, Field = "AU_CO", sep = ";")

bib_concolab_NetMatrix <- biblioNetwork(bib_concolab, analysis = "collaboration",
                                       network = "countries", sep = ";")

bib_concolab_Plot <- networkPlot(bib_concolab_NetMatrix, 
                                 n = dim(bib_concolab_NetMatrix)[1], 
                                 Title = "Country collaboration",type = "circle", 
                                 size=10, size.cex=T, edgesize = 1.5, labelsize=1,
                                 cluster = "none")
```


## Institution

The collaboration network between the institution was shown in @fig-bib_EduColabPlot.

```{r}
#| label: fig-bib_EduColabPlot
#| fig-cap: "Institution Collaboration Map"
#| column: screen-inset-shaded
#| fig-width: 10
#| fig-height: 7

bib_educolab_NetMatrix <- biblioNetwork(bibds_wos, analysis = "collaboration",
                                       network = "universities", sep = ";")

bib_educolab_Plot <- networkPlot(bib_educolab_NetMatrix, n = 25, 
                                 cluster = "optimal", type = "auto",
                                 size.cex = F, size = 4, remove.multiple = F,
                                 labelsize=1, alpha = .7, edgesize = 5,
                                 Title = "Institutions collaboration")
```


## Journals






## Authors, Articles and References

Out of total `r sum(bibres_autable$Np)` authors, majority of them appear once (`r max(bibres_autablepercent$percent)`%), while `r bibres_autablepercent$percent[2]`% of the authors had produced 2 publications, `r bibres_autablepercent$percent[3]`% and `r bibres_autablepercent$percent[4]`% produced 3 and 4 publication respectively. The top 5 productive authors as shown in @tbl-top5authors.


```{r}
#| label: tbl-top5authors
#| tbl-cap: "Most Productive Authors"

bibres_autable %>% 
  rename("Number of Publications" = "Np") %>% 
  mutate(Author = str_to_title(Author)) %>% 
  head(n = 5) %>% 
  kable() %>% kable_classic(full_width = F)

```

All articles were subjected to a author coupling analysis to produce the network map, as shown in @fig-bib_AuCoupling_Plot. The connection between two nodes indicates that the articles have a common references, and the wieghting reflect the coupling strenght of the two nodes 

```{r}
#| label: fig-bib_AuCoupling_Plot
#| fig-cap: "Author Coupling Analysis"
#| column: screen-inset-shaded
#| fig-width: 10
#| fig-height: 7

bib_AuCoupling_NetMatrix <- biblioNetwork(bibds_wos, analysis = "coupling",
                                          network = "authors", sep = ";")

bib_AuCoupling_Plot <- networkPlot(bib_AuCoupling_NetMatrix, n = 20, 
                                   cluster = "optimal", type = "auto", 
                                   size.cex = T, size = 20, remove.multiple = F,
                                   Title = "Bibliographic coupling of the authors",
                                   alpha = .7)
```



















```{r}
#| label: working
#| include: false

# bibres_aulist <- bibres$Authors
# 
# nrow(bibres$Authors)
# 
# tibble(Rank = seq_along(bibres_aulist),
#        Author = rownames(bibres_aulist),
#        `Number of Publications` = bibres_aulist)
# 
# bibres_journallist <- bibres$Sources
# 
# nrow(bibres$Sources)
# 
# tibble(Rank = seq_along(bibres_journallist),
#        `Sources (Journal)` = rownames(bibres_journallist),
#        `Number of Publications` = bibres_journallist)
# 
# bibres$TotalCitation %>% sum()
# 
# bibres_journallist <- bibres$Sources
# 
# nrow(bibres$Sources)
# 
# tibble(Rank = seq_along(bibres_journallist),
#        `Sources (Journal)` = rownames(bibres_journallist),
#        `Number of Publications` = bibres_journallist)


```







```{r}
#| label: tbl-top10institution
#| tbl-cap: "Most Productive Institution"

bibres_instlist <- bibres$Affiliations

tibble(Rank = seq_along(bibres_instlist),
  `Institution name` = rownames(bibres_instlist),
       `Number of Publications` = bibres_instlist) %>% 
  filter(`Number of Publications` >= 5) %>% 
  kable() %>% kable_classic(full_width = F)
```


```{r}
bib_kwco_NetMatrix <- biblioNetwork(bibds_wos, analysis = "co-occurrences", 
                                     network = "keywords", sep = ";")

bib_kwco_Plot <- networkPlot(bib_kwco_NetMatrix, normalize = "association", 
                             n = 25, Title = "Keyword Co-occurences", 
                             cluster = "optimal", type = "fruchterman", 
                             size.cex = T, size = 20,  remove.multiple = F, 
                             edgesize = 7, labelsize = 3, label.cex = T, 
                             label.n = 20, edges.min = 5)

```








# Discussion

# Conclusion
